---
title: "CodeForMachineLearningFormat"
author: "Kirk Geier"
date: "June 28, 2017"
output: html_document
---

Load Packages
```{r}
library("broom", lib.loc="~/R/R-3.3.1/library")
library("tidyr", lib.loc="~/R/R-3.3.1/library")
library("ggplot2", lib.loc="~/R/R-3.3.1/library")
library("gridExtra", lib.loc="~/R/R-3.3.1/library")
library("dplyr", lib.loc="~/R/R-3.3.1/library")
library("tidyr", lib.loc="~/R/R-3.3.2/library")
library("plotly", lib.loc="~/R/R-3.3.2/library")
library(plyr)
library(data.table)
library(reshape2)
library(readr)
```


```{r}
#note, 9a and 9b were combined in advance to this. 9a block 11 crashed part way through. 

i=1
for (i in 1:37){
  data_dir = 'C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/EyeTracking/ObjFamETStudy/MACHINE_LEARNING_codeForPradeep/SampleReportsAll' 
  filename =  i
  fileextension = ".csv"
  filename = paste0(filename, fileextension)
  filepath = paste(data_dir, '/', filename, sep = ''); filepath
  
  test <- fread(filepath)
  
}


```











MACHINE_LEARNING_codeForPradeep/SampleReportsAll
Define some paths
```{r}
  data_dir = 'C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/EyeTracking/ObjFamETStudy/MACHINE_LEARNING_codeForPradeep/SampleReportsAll' 
  filename =  'sample_report_*.csv' 
  filepath = paste(data_dir, '/', filename, sep = ''); filepath
```
Read in Data
```{r}

df.list <- list(1:37)

```

j = 1 
for (i in df.list){
  mainDir <- "C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/MAYO/R studio analysis/design.files"
  subDir <- i
  path <- file.path(mainDir,subDir)
  dir.create(path, showWarnings = FALSE)
  write.csv(x=df.list[[j]], file= paste0(path,"/","design.csv"), row.names = FALSE)
  j= j+1
}
#subj2001
mainDir <- "C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/MAYO/R studio analysis/design.files"
subDir <- 2001
path <- file.path(mainDir,subDir)
dir.create(path, showWarnings = FALSE)
write.csv(x=df.list[[25]], file= paste0(path,"/","design.csv"), row.names = FALSE)

#writing file for df.final (design file not separated by subj)
mainDir <- "C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/MAYO/R studio analysis/design.files"
subDir <- "all24"
path <- file.path(mainDir,subDir)
dir.create(path, showWarnings = FALSE)
write.csv(x=df.final, file= paste0(path,"/","designAll.csv"), row.names = FALSE)





foreach($file in (Get-ChildItem "C:/Users/kgeier/Google Drive/OlsenLab_cloud/All Experiments/EyeTracking/ObjFamETStudy/MACHINE_LEARNING_codeForPradeep/SampleReportsAll")) {

  $newname = $file.FullName -replace '\.xls$', '.csv'
  $ExcelWB = new-object -comobject excel.application
  $Workbook = $ExcelWB.Workbooks.Open($file.FullName) 
  $Workbook.SaveAs($newname,6)
  $Workbook.Close($false)
  $ExcelWB.quit()

}

